String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-08-02 2023-1-19/sections/conclusion.tex
grammerly check

%TODO
This work proposes an efficient automata-theoretical approach for solving RECL constraints, that is, string constraints with regex-counting and string-length. The approach is based on the idea of encoding counting operators in regular expressions by registers symbolically, instead of unfolding them explicitly. Moreover, this paper proposes an automata-size reduction technique and an under-approximation based solution searching technique to improve the performance. Finally, we use two benchmark suites comprising 48,834 instances in total to evaluate the performance of our approach. The experimental results show that our approach can solve more instances than the state-of-the-art best solvers on RECL constraints, with a comparable performance. For the future work, we plan to investigate symbolic approaches to dealing with nested counting operators.

>>>>

%TODO
This work proposes an efficient automata-theoretical approach for solving RECL constraints: string constraints with regex-counting and string-length. The approach is based on encoding counting operators in regular expressions by registers symbolically instead of unfolding them explicitly. Moreover, this paper proposes an automata-size reduction technique and an under-approximation-based solution searching technique to improve performance. Finally, we use two benchmark suites comprising 48,834 instances in total to evaluate the performance of our approach. The experimental results show that our approach, with comparable performance, can solve more instances than the state-of-the-art best solvers on RECL constraints. We plan to investigate symbolic approaches to dealing with nested counting operators in future work.

### 2023-08-02 2023-1-19/sections/implementation.tex
typo removement
grammerly check

We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{ostrich,atva2020}, resulting in a version of OSTRICH called $\ostrichrecl$.
Then we do experiments on two benchmark suites, to evaluate the performance of $\ostrichrecl$. In the sequel, we first describe the two benchmark suites, then present the settings and results of the experiments.

@@

\medskip
\noindent
\emph{RegCoL benchmark suite.} There are 40,628 RECL constraints in the RegCoL suite. These constraints are generated by extracting regular expressions with counting operators from the open source regex library \cite{regex_lingua_franca,redos_lenka} and constructing for each regular expression $e$ a RECL constraint of the form 
$x \in e \wedge x \in \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*} \wedge |x| > 10,$   
where $\Sigma^*(<+ >+'+''+\&)\Sigma^*$ is a regular expression that specifies at least one occurrence of special characters $<$, $>$, $'$, $''$, or $\&$, and $\overline{e'}$ denotes the complement of a regular expression $e'$. 
%We would like to remark that there are about 500,000 real-world regular expressions in \cite{regex_lingua_franca,redos_lenka} and regular expressions with counting operators occupy about 8\% of them. 
Moreover, among these 40,628 RECL constraints, only 5\% of them include non-register-representable regexes.

\medskip
\noindent
\emph{AutomatArk benchmark suite.}
The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraint $|x| > 10$ (where $x$ is a string variable). There are 8,215 instances in the AutomatArk suite here.
Note that the original AutomatArk benchmark suite in \cite{z3str3re} includes 19,979 instances in total, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}. 
%Only 8,751 ones that contain counting operators out of 19,979 instances.

%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
\hide{
We conducted a comparison on four sets of benchmarks based on regex with 
counting operator, consisting of a total of 49,379 instances. We analyze all 19 developed benchmarks listed in \cite{zaligvinder_2021} and find that only \textbf{AutomatArk} benchmarks have regular membership with counting operator. In total, almost 18\% of the instances we evaluated were sourced from published industrial benchmarks or other solver developers. The other instances are generated by ourselves with regular expressions from real world. Each set of the benchmark is evenly divided into "large" and "small": the "large" set contains instances with large upper bounds of counting operator (the sum of upper bounds is greater than 50), and "small" contains remained instances. About 10\% of the benchmarks are in a "large" set. More details about the benchmarks are shown below.

\subsubsection{AutomatArk} is the 8,751 instances generated by Berzish et al.\cite{z3str3re}. It is based on real-world regular expression queries from Loris D'Antoni\cite{automatark}. The origin set comprises two tracks, a simple and a hard track, with 19,979 instances. The simple track contains instances with a single regular expression membership constraint, whereas the hard track can hold up to five membership constraints for a single variable per instance. We extract 8,751 instances containing counting operator.

@@

\subsubsection{RegexLib} is the set of 1,623 instances we generated similarly to the \textbf{ReDos} benchmark. It is based on the regular expressions collected by James C. Davis et al.\cite{regex_lingua_franca} from regex lib website\cite{regexlib}. The website is the Internet's first Regular Expression Library. Currently, it has indexed 4149 expressions from 2818 contributors around the world since 2001. We extract 1,623 instances containing bounded repetition from 4149 instances. The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.

\subsubsection{StackOverflow} is the 37381 instances we generated similarly to the \textbf{ReDos} benchmark. As the Regexlib benchmark, the real-world regex expressions are collected by James C. Davis et al.\cite{regex_lingua_franca} from StackOverflow website\cite{stackoverflow}. The website is a question-and-answer site for professional and enthusiast programmers. We extract 37,381 instances containing bounded repetition from almost 500,000 instances. The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.
\begin{equation} \label{eq:template}
  x\in \regex \wedge x\not\in \Sigma^*(<\mid >\mid '\mid ''\mid \&)\Sigma^*\wedge |x| > 50(or \ 20)
\end{equation}
}
%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%

@@

The experiment results on the RegCol benchmark suite are put in Table~\ref{tab:results_regcol}. 
From Table~\ref{tab:results_regcol}, we can see that $\ostrichrecl$ solvers almost all 40,628 instances, except 106 of them, that is, it solves 40,522 instances correctly, which is %3,994/2,272/24,577/12,832/1,091/7,092 
3,893/2,081/20,483/10,200/1,082/5,505 more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
%    
Note that the solvers  Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth\footnote{Although it seems a bit strange to use one solver as the ground truth, this is the practice for string constraint solving, since CVC5 is the most stable string solver at present.}. If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance. 
%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
%
Moreover, $\ostrichrecl$ is the second fastest solver. More specifically, $\ostrichrecl$ spends 3.02 seconds per instance on average, while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.56 seconds per instance.  
Note that Z3-Trau reports ``unknown'' on 21,655 instances, which seems to be mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.

@@

The experiment results on the AutomatArk benchmark suite are put in Table~\ref{tab:results_automatark}. 
From Table~\ref{tab:results_automatark}, we can see that $\ostrichrecl$ solvers almost all 8,215 instances, except 39 of them, that is, it solves 8,176 instances correctly, which is %3,994/2,272/24,577/12,832/1,091/7,092 
101/191/4,094/2,632/9/1,587
more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
%    
Still the soundness errors are reported by taking the results of CVC5 as the ground truth.
%Note that Z3-Trau has soundness errors, where the result of CVC5 is taken as the ground truth. If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance. 
%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
%
Moreover, $\ostrichrecl$ spends 2.49 seconds per instance on average. 
%while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.49 seconds per instance.  
%Note that Z3-Trau reports ``unknown'' on 2,552 instances, which seems to be mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.

In summary, $\ostrichrecl$ solves 48,698 out of 48,834 instances, which is 1,091 more than Z3str3RE, the state-of-the-art best solver on RECL constraints. Moreover, the speed of $\ostrichrecl$ is the second fastest and comparable to that of Z3str3RE. (See Table~\ref{tab:results_summary}.)

@@

To answer Q2, we compare OSTRICH$^{\rm RECL}$ with its three variants, namely, OSTRICH$^{\rm RECL}$ where the size-reduction, under-approximation, or both are removed. 
For convenience, let us use OSTRICH$^{\rm RECL^-}$ to denote the variant of OSTRICH$^{\rm RECL}$ that both size-reduction and under-approximation techniques are removed, 
OSTRICH$^{\rm RECL^-}_{+\rm SR}$ (resp. OSTRICH$^{\rm RECL^-}_{+\rm UA}$) to denote the variant that is obtained by adding the size-reduction (resp. under-approximation) techniques to OSTRICH$^{\rm RECL^-}$.
%OSTRICH$^{\rm RECL}_{\rm -SR}$, OSTRICH$^{\rm RECL}_{\rm -UA}$, OSTRICH$^{\rm RECL}_{\rm -SRUA}$, which remove size-reduction, under-approximation, and both from OSTRICH$^{\rm RECL}$ respectively. 
The experiment results can be found in Table~\ref{tab:results_heuristics}.
From Table~\ref{tab:results_heuristics}, we can see that adding size-reduction techniques help to solve 1,563 more instances and reduce the average time per instance for 46.4\% (see the OSTRICH$^{\rm RECL^-}_{\rm +SR}$ column), while adding under-approximation techniques help to solve 1,476 more instances and reduce the average time per instance for 42.7\% (see the OSTRICH$^{\rm RECL^-}_{\rm +UA}$ column), moreover, adding both help to solve 1,579 more instances and reduce the average time per instance for 46.5\% (see the OSTRICH$^{\rm RECL}$ column). Note that adding under-approximation to OSTRICH$^{\rm RECL^-}_{\rm +SR}$ help to solve 19 more sat instances, while reduces the number of solved unsat instances by 3, since under approximation techniques do not help to solve unsat instances.
}
%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
%Moreover, adding these techniques also decrease the average time spent in solving each instance considerably.

@@

%%%%%%%%%% original texts by denghang %%%%%%%%%
%%%%%%%%%% original texts by denghang %%%%%%%%%
\hide{
%
We have evaluated OstrichCEA compared to five other prominent string solvers currently available. We evaluate the solvers by directly comparing the number of cases correctly solved, the average time taken with and without timeouts, and the total count of soundness errors and program crashes. One of these solvers is CVC5\cite{cvc5}, a general SMT solver that uses algebraic reasoning to handle strings and regular expressions and is the winner of SMT-COMP 2022\cite{smt-comp}. Another solver, Z3str3\cite{z3str3}, is the most recent addition we can get to the Z3-str family and utilizes a word equation reduction approach to reason about regular expressions. Z3str3RE\cite{z3str3re} is a variant of Z3str3 that incorporates length-aware algorithms and heuristics. Z3seq\cite{z3seq} is a sequence solver which uses a novel derivative theory for solving extended regular expressions. Z3-Trau\cite{z3trau} is the Z3 version of trau\cite{trau} that employs a flat automata-based approach, incorporating both under- and over-approximations. Ostrich\cite{ostrich} is the tool we extend which uses automaton to model the semantics of string functions and regular memberships. We used the 1.0.5 binary version of CVC5, commit 59e9c87 of Z3str3, last version of Z3str3RE, 4.8.9 binary version of Z3Seq, commit 1628747 of Z3-Trau and commit 8297d8d of Ostrich. Z3-Trau does not support \verb|re.diff|. All other solvers support all syntax sugars listed in SMT-LIB standard\cite{smt_lib}. We omitted Z3str4\cite{z3str4} because the provided reproduction package link is wrong. All experiments are conducted on CentOS Stream release 8 with 12 Intel(R) Xeon(R) Platinum 8269CY CPU T 3.10GHz processors and 190 GB memory. We used Zaligvinder\cite{zaligvinder_2021} framework and set the timeout to 60 seconds.

%\subsection{Overall Evaluation}
In Fig.\ref{fig:cactus_all}, the cactus plot illustrates the cumulative time each solver takes for all cases in ascending order of runtime. Solvers located towards the right and lower portion of the plot indicate better performance. \newline
Table \ref{tab:results_all} summarizes the results that demonstrate OstrichCEA's superior performance, solving the most significant number of instances and outperforming most competing solvers. Including timeouts, OstrichCEA is \textbf{1.52}\mult{} faster than Z3Seq, \textbf{2.23}\mult{} faster than Ostrich, \textbf{2.26}\mult{} faster than Z3-Trau, \textbf{3.08}\mult{} faster than Z3str3, \textbf{3.11}\mult{} faster than CVC5 and close to Z3str3RE with \%2 speed loss . Note that CVC5\cite{cvc5} yielded 5370 timeouts(11\% of all instances), and Z3str3\cite{z3str3} yielded 6139 timeouts(12\% of all instances), which is much more than other solvers. Both CVC5 and Z3str3 are DPLL(T)-based solvers. It seems that almost 10\% of the benchmarks we used seem unsuitable for them. Z3-trau\cite{z3trau} yielded 21,152 unknowns because it does not support \verb|re.diff|. Z3-trau\cite{z3trau} yielded 6673 crashes (13\% of the instances) and 1233 soundness errors (2\% of the instances), which is a large portion. Z3-based solvers Z3str3 yielded 38 soundness errors, Z3seq\cite{z3seq} yielded 51 soundness errors and Z3str3RE\cite{z3str3re} yielded 39 soundness error. Most of them are due to the mistake formalization of the backslash character. OstrichCEA resulted 5 unknowns because it reached the maximum threshold of limited memory 2GB. More details of the results of each benchmark are shown in \ref{appendix:experiential_results}.
\begin{figure}[h]
  \centering
  \import{figures}{cactus_plot_all.tex}
  \caption{Cactus plot summarizing performance on all benchmarks.}
  \label{fig:cactus_all}
\end{figure}

%\subsection{Analysis of Individual Heuristics}
In order to demonstrate the efficacy of the individual heuristics outlined in Section \ref{sec:algorithm} and incorporated into OstrichCEA, we assessed various tool configurations in which one or more heuristics were disabled. Figure \ref{fig:cactus_heuristics} and Table \ref{tab:results_heuristics} display the outcomes. The "OstrichCEA" plot line represents the tool's performance when all heuristics are enabled, while the "All heuristics off" line represents performance when all heuristics are disabled. The remaining plot lines exhibit performance with only the named heuristic disabled while all others are enabled. From the plots and table, it is evident that OstrichCEA functions most effectively when all heuristics are enabled. In average time with timeout times, OstrichCEA performs \textbf{1.78}$\times$ faster than employing none of our heuristics, \textbf{1.37}$\times$ faster than turning off simplification, \textbf{1.15}$\times$ faster than truing off under-approximation.
\begin{figure}
  \subimport{figures/}{cactus_plot_heuristic.tex}
  \caption{A performance comparison was made on all benchmarks by disabling individual heuristics using a cactus plot.}
  \label{fig:cactus_heuristics}
\end{figure}
\begin{table}
  \subimport{tables}{table_heuristic.tex}
  \caption{A performance comparison was made on all benchmarks by disabling individual heuristics.}
  \label{tab:results_heuristics}
\end{table}
}
%%%%%%%%%% original texts by denghang %%%%%%%%%
%%%%%%%%%% original texts by denghang %%%%%%%%%
%\end{document}

>>>>

We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{Ostrich,atva2020}, resulting in a version of OSTRICH called $\ostrichrecl$.
Then we do experiments on two benchmark suites to evaluate the performance of $\ostrichrecl$. In the sequel, we first describe the two benchmark suites, then present the settings and results of the experiments.

@@

\medskip
\noindent
\emph{RegCoL benchmark suite.} There are 40,628 RECL constraints in the RegCoL suite. These constraints are generated by extracting regular expressions with counting operators from the open source regex library \cite{regex_lingua_franca,redos_lenka} and constructing for each regular expression $e$ a RECL constraint of the form 
$x \in e \wedge x \in \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*} \wedge |x| > 10,$   
where $\Sigma^*(<+ >+'+''+\&)\Sigma^*$ is a regular expression that specifies at least one occurrence of special characters $<$, $>$, $'$, $''$, or $\&$, and $\overline{e'}$ denotes the complement of a regular expression $e'$. 
%We would like to remark that there are about 500,000 real-world regular expressions in \cite{regex_lingua_franca,redos_lenka} and regular expressions with counting operators occupy about 8\% of them.

\medskip
\noindent
\emph{AutomatArk benchmark suite.}
The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraint $|x| > 10$ (where $x$ is a string variable). There are 8,215 instances in the AutomatArk suite here.
Note that the original AutomatArk benchmark suite in \cite{z3str3re} includes 19,979 instances in total, conjunctions of regular membership queries generated out of regular expressions from \cite{automatark}. 
%Only 8,751 ones that contain counting operators out of 19,979 instances.

Moreover, among the 48,834 RECL constraints in the RegCoL or AutomatArk suite, only 5\% of them include non-register-representable regexes.

%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
\hide{
We conducted a comparison on four sets of benchmarks based on regex with 
counting operator, consisting of a total of 49,379 instances. We analyze all 19 developed benchmarks listed in \cite{zaligvinder_2021} and find that only \textbf{AutomatArk} benchmarks have regular membership with the counting operator. In total, almost 18\% of the instances we evaluated were sourced from published industrial benchmarks or other solver developers. The other instances are generated by ourselves with regular expressions from the real world. Each set of the benchmark is evenly divided into "large" and "small": the "large" set contains instances with large upper bounds of the counting operator (the sum of upper bounds is greater than 50), and "small" contains remaining instances. About 10\% of the benchmarks are in a "large" set. More details about the benchmarks are shown below.

\subsubsection{AutomatArk} is the 8,751 instances generated by Berzish et al.\cite{z3str3re}. It is based on real-world regular expression queries from Loris D'Antoni\cite{automatark}. The origin set comprises two tracks, a simple and a hard track, with 19,979 instances. The simple track contains instances with a single regular expression membership constraint, whereas the hard track can hold up to five membership constraints for a single variable per instance. We extract 8,751 instances containing counting operators.

@@

\subsubsection{RegexLib} is the set of 1,623 instances we generated similarly to the \textbf{ReDos} benchmark. It is based on the regular expressions collected by James C. Davis et al.\cite{regex_lingua_franca} from regex lib website\cite{regexlib}. The website is the Internet's first Regular Expression Library. Currently, it has indexed 4149 expressions from 2818 contributors around the world since 2001. We extracted 1,623 instances containing bounded repetition from 4149 instances. The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.

\subsubsection{StackOverflow} is the 37381 instances we generated similarly to the \textbf{ReDos} benchmark. As the Regexlib benchmark, the real-world regex expressions are collected by James C. Davis et al.\cite{regex_lingua_franca} from StackOverflow website\cite{stackoverflow}. The website is a question-and-answer site for professional and enthusiast programmers. We extracted 37,381 instances containing bounded repetition from almost 500,000 instances. The length lower bound is set to $20$ for the "small" set and $50$ for the "large" set.
\begin{equation} \label{eq:template}
  x\in \regex \wedge x\not\in \Sigma^*(<\mid >\mid '\mid ''\mid \&)\Sigma^*\wedge |x| > 50(or \ 20)
\end{equation}
}
%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%
%%%%%%%%%%%%%%%%%% the benchmark suite written by Denghang %%%%%%%%%%%

@@

The RegCol benchmark suite's experiment results are in Table~\ref{tab:results_regcol}. 
From Table~\ref{tab:results_regcol}, we can see that $\ostrichrecl$ solvers almost all 40,628 instances, except 106 of them, that is, it solves 40,522 instances correctly, which is %3,994/2,272/24,577/12,832/1,091/7,092 
3,893/2,081/20,483/10,200/1,082/5,505 more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
%    
Note that the solvers  Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth\footnote{Although it seems strange to use one solver as the ground truth, this is the practice for string constraint solving, since CVC5 is the most stable string solver at present.}. If CVC5 reports ``unknown'' or ``timeout'' in some instances, then no soundness errors will be reported in this instance. 
%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
%
Moreover, $\ostrichrecl$ is the second fastest solver. More specifically, $\ostrichrecl$ spends 3.02 seconds per instance on average, while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.56 seconds per instance.  
Note that Z3-Trau reports ``unknown'' on 21,655 instances, which seems mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.

@@

The experiment results on the AutomatArk benchmark suite are put in Table~\ref{tab:results_automatark}. 
From Table~\ref{tab:results_automatark}, we can see that $\ostrichrecl$ solvers almost all 8,215 instances, except 39 of them, that is, it solves 8,176 instances correctly, which is %3,994/2,272/24,577/12,832/1,091/7,092 
101/191/4,094/2,632/9/1,587
more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
%    
Still, the soundness errors are reported by taking the results of CVC5 as the ground truth.
%Note that Z3-Trau has soundness errors, where the result of CVC5 is taken as the ground truth. If CVC5 reports ``unknown'' or ``timeout'' in some instances, then no soundness errors will be reported in this instance. 
%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
%
Moreover, $\ostrichrecl$ spends 2.49 seconds per instance on average. 
%while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.49 seconds per instance.  
%Note that Z3-Trau reports ``unknown'' on 2,552 instances, which seems to be mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.

In summary, $\ostrichrecl$ solves 48,698 out of 48,834 instances, 1,091 more than Z3str3RE, the state-of-the-art best solver on RECL constraints. Moreover, the speed of $\ostrichrecl$ is the second fastest and comparable to that of Z3str3RE. (See Table~\ref{tab:results_summary}.)

@@

To answer Q2, we compare OSTRICH$^{\rm RECL}$ with its three variants, namely, OSTRICH$^{\rm RECL}$ where the size-reduction, under-approximation, or both are removed. 
For convenience, let us use OSTRICH$^{\rm RECL^-}$ to denote the variant of OSTRICH$^{\rm RECL}$ that both size-reduction and under-approximation techniques are removed, 
OSTRICH$^{\rm RECL^-}_{+\rm SR}$ (resp. OSTRICH$^{\rm RECL^-}_{+\rm UA}$) to denote the variant that is obtained by adding the size-reduction (resp. under-approximation) techniques to OSTRICH$^{\rm RECL^-}$.
%OSTRICH$^{\rm RECL}_{\rm -SR}$, OSTRICH$^{\rm RECL}_{\rm -UA}$, OSTRICH$^{\rm RECL}_{\rm -SRUA}$, which remove size-reduction, under-approximation, and both from OSTRICH$^{\rm RECL}$ respectively. 
The experiment results can be found in Table~\ref{tab:results_heuristics}.
From Table~\ref{tab:results_heuristics}, we can see that adding size-reduction techniques help to solve 1,563 more instances and reduce the average time per instance for 46.4\% (see the OSTRICH$^{\rm RECL^-}_{\rm +SR}$ column), while adding under-approximation techniques help to solve 1,476 more instances and reduce the average time per instance for 42.7\% (see the OSTRICH$^{\rm RECL^-}_{\rm +UA}$ column), moreover, adding both help to solve 1,579 more instances and reduce the average time per instance for 46.5\% (see the OSTRICH$^{\rm RECL}$ column). Note that adding under-approximation to OSTRICH$^{\rm RECL^-}_{\rm +SR}$ helps to solve 19 more sat instances while reducing the number of solved unsat instances by 3 since under approximation techniques do not help to solve unsat instances.
}
%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
%Moreover, adding these techniques also decrease the average time spent in solving each instance considerably.

@@

%%%%%%%%%% original texts by denghang %%%%%%%%%
%%%%%%%%%% original texts by denghang %%%%%%%%%
\hide{
%
We have evaluated OstrichCEA compared to five other prominent string solvers currently available. We evaluate the solvers by directly comparing the number of cases correctly solved, the average time taken with and without timeouts, and the total count of soundness errors and program crashes. One of these solvers is CVC5\cite{cvc5}, a general SMT solver that uses algebraic reasoning to handle strings and regular expressions and is the winner of SMT-COMP 2022\cite{smt-comp}. Another solver, Z3str3\cite{z3str3}, is the most recent edition we can get to the Z3-str family and utilizes a word equation reduction approach to reason about regular expressions. Z3str3RE\cite{z3str3re} is a variant of Z3str3 that incorporates length-aware algorithms and heuristics. Z3seq\cite{z3seq} is a sequence solver which uses a novel derivative theory for solving extended regular expressions. Z3-Trau\cite{z3trau} is the Z3 version of trau\cite{trau} that employs a flat automata-based approach, incorporating both under- and over-approximations. Ostrich\cite{Ostrich} is the tool we extend which uses automaton to model the semantics of string functions and regular memberships. We used the 1.0.5 binary version of CVC5, commit 59e9c87 of Z3str3, the last version of Z3str3RE, 4.8.9 binary version of Z3Seq, commit 1628747 of Z3-Trau and commit 8297d8d of Ostrich. Z3-Trau does not support \verb|re.diff|. All other solvers support all syntax sugars listed in SMT-LIB standard\cite{smt_lib}. We omitted Z3str4\cite{z3str4} because the provided reproduction package link is wrong. All experiments are conducted on CentOS Stream release 8 with 12 Intel(R) Xeon(R) Platinum 8269CY CPU T 3.10GHz processors and 190 GB memory. We used Zaligvinder\cite{zaligvinder_2021} framework and set the timeout to 60 seconds.

%\subsection{Overall Evaluation}
In Fig.\ref{fig:cactus_all}, the cactus plot illustrates the cumulative time each solver takes for all cases in ascending order of runtime. Solvers located towards the right and lower portion of the plot indicate better performance. \newline
Table \ref{tab:results_all} summarizes the results demonstrating OstrichCEA's superior performance, solving the most significant number of instances and outperforming most competing solvers. Including timeouts, OstrichCEA is \textbf{1.52}\mult{} faster than Z3Seq, \textbf{2.23}\mult{} faster than Ostrich, \textbf{2.26}\mult{} faster than Z3-Trau, \textbf{3.08}\mult{} faster than Z3str3, \textbf{3.11}\mult{} faster than CVC5 and close to Z3str3RE with \%2 speed loss . Note that CVC5\cite{cvc5} yielded 5370 timeouts(11\% of all instances), and Z3str3\cite{z3str3} yielded 6139 timeouts(12\% of all instances), which is much more than other solvers. Both CVC5 and Z3str3 are DPLL(T)-based solvers. It seems that almost 10\% of the benchmarks we used seem unsuitable for them. Z3-trau\cite{z3trau} yielded 21,152 unknowns because it does not support \verb|re.diff|. Z3-trau\cite{z3trau} yielded 6673 crashes (13\% of the instances) and 1233 soundness errors (2\% of the instances), which is a large portion. Z3-based solvers Z3str3 yielded 38 soundness errors, Z3seq\cite{z3seq} yielded 51 soundness errors and Z3str3RE\cite{z3str3re} yielded 39 soundness error. Most of them are due to the mistake of formalization of the backslash character. OstrichCEA resulted in 5 unknowns because it reached the maximum threshold of limited memory 2GB. More details of the results of each benchmark are shown in \ref{appendix:experiential_results}.
\begin{figure}[h]
  \centering
  \import{figures}{cactus_plot_all.tex}
  \caption{Cactus plot summarizing performance on all benchmarks.}
  \label{fig:cactus_all}
\end{figure}

%\subsection{Analysis of Individual Heuristics}
In order to demonstrate the efficacy of the individual heuristics outlined in Section \ref{sec:algorithm} and incorporated into OstrichCEA, we assessed various tool configurations in which one or more heuristics were disabled. Figure \ref{fig:cactus_heuristics} and Table \ref{tab:results_heuristics} display the outcomes. The "OstrichCEA" plot line represents the tool's performance when all heuristics are enabled, while the "All heuristics off" line represents performance when all heuristics are disabled. The remaining plot lines exhibit performance with only the named heuristic disabled while all others are enabled. The plots and table show that OstrichCEA functions most effectively when all heuristics are enabled. In average time with timeout times, OstrichCEA performs \textbf{1.78}$\times$ faster than employing none of our heuristics, \textbf{1.37}$\times$ faster than turning off simplification, \textbf{1.15}$\times$ faster than truing off under-approximation.
\begin{figure}
  \subimport{figures/}{cactus_plot_heuristic.tex}
  \caption{A performance comparison was made on all benchmarks by turning off individual heuristics using a cactus plot.}
  \label{fig:cactus_heuristics}
\end{figure}
\begin{table}
  \subimport{tables}{table_heuristic.tex}
  \caption{A performance comparison was made on all benchmarks by turning off individual heuristics.}
  \label{tab:results_heuristics}
\end{table}
}
%%%%%%%%%% original texts by denghang %%%%%%%%%
%%%%%%%%%% original texts by denghang %%%%%%%%%
%\end{document}
